The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-03-21 ms.Rmd
adding a first attempt at a programmtic workflow illustration

```{r, echo = FALSE, fig.cap = "The modular SDM structure encoded by a zoon workflow. A) Flow diagram representing the module types. B) The required inputs and outputs for each module types (full details given in the `zoon` vignette 'Building a module'). C) Chaining and listing modules of the same type. D) The structure of a workflow object.\\label{fig:workflows}"}

# four panel plot, no margins
par(mar = c(1, 1, 2, 1),
    mfrow = c(2, 2))

# placeholder plots for each panel
for (i in 1:4) {

>>>>

```{r, echo = FALSE, fig.height = 9, fig.cap = "The modular SDM structure encoded by a zoon workflow. A) Flow diagram representing the module types. B) The required inputs and outputs for each module types (full details given in the `zoon` vignette 'Building a module'). C) Chaining and listing modules of the same type. D) The structure of a workflow object.\\label{fig:workflows}"}

# four panel plot
par(mfrow = c(2, 2))

#plot the saved image in the first panel
library(raster)
r <- brick('figs/workflow_basic.png')
par(mar = c(1, 1, 2, 1))
plotRGB(r, maxpixels = Inf)

# add a panel letter
# this is an awful hack and completely contingent on the screenshot size :/
text(40, 980, labels = LETTERS[1],
      xpd = NA,
     cex = 1.2)

par(mar = c(1, 1, 2, 1))
# placeholder plots for each panel
for (i in 2:4) {
